On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
l1 ramble

>>>>

Solving Prob.~\ref{SLCopt} directly is intractable in general since it necessitates, for each proposed dictionary $\mathbf{B}$, a combinatorial search for the supports of the associated sparse codes $\mathbf{\overline x}_i$. A common work-around is to convexify the problem (for fixed $\mathbf{B}$) by substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$, impelled the fact that matrices $\mathbf{A}$ with large enough $L_{2k}(\mathbf{A})$ induce the same sparse codes via minimization of either norm \cite{?}. To this end, the lower bound $L_{2k}(\mathbf{BP}) \geq (L_{2k}(\mathbf{A}) - C_1\varepsilon) / \|\mathbf{D}\|_1$ implied by Thm.~\ref{DeterministicUniquenessTheorem} hints at conditions on the generating dictionary $\mathbf{A}$ and $k$-sparse codes $\mathbf{x}_i$ under which \emph{all} matrices $\mathbf{B}$ (of bounded column-norm) that solve Prob.~\ref{OptimizationProblem} also share this property of $\mathbf{A}$ by virtue of uniqueness and stability. One might then imagine an inference procedure whereby sparse codes are inferred via minimization of $\|\cdot\|_1$, but solutions still evaluated by their collective support size, yielding unique optimal solutions to Prob.~\ref{SLCopt} if only constraints could be imposed such that the learning procedure eventually guides $\mathbf{B}$ through an optimal dictionary. % (e.g. the dictionary is a member of a known finite set).
